Investigating soundscapes perception through acoustic scenes simulation

### 2018-06-26 v2/responseToReviewers.tex

\item \emph{please follow APA (American Psychological Association) style guidelines (w.r.t. in-text citations, etc.).}

$\rightarrow$ The manuscript now follows the APA citation style. The text have been modified accordingly.

\item \emph{ Please avoid the over-use of acronyms as it makes reading of your article unnecessarily difficult (examples: P@5, ni, i, etc.). This sort of lab jargon is not transparent to the wider readership of BRM. }

$\rightarrow$ Those abbreviations are now in full text, except for some figures for the sake of clarity, in which case the acronyms used are detailed in the caption.

@@

\item \emph{I would also like to see comparisons between your approach and other state-of-the-art soundscape analyses (e.g. TAPESTREA, see comment from the reviewer below).}

$\rightarrow$ The work of Misra \& al is indeed very relevant. A new Section (number 6) is now dedicated to this comparison with state-of-the-art approaches.

@@

\item \emph{You might consider providing a link to a github site with examples of your stimuli. It is hard to imagine what these sound scenes sound like without some real examples.}

$\rightarrow$ The resulting waveforms are available for download \url{https://archive.org/details/soundSimulatedUrbanScene}. The link is now in the introduction. The software platform used for the experiment, the parametrization of the software platform for each generated scene, as well as a 2 dimensional projection of the resulting scenes are available \url{http://soundthings.org/research/urbanSoundScape/XP2014}.

@@

\end{enumerate}

\section{Answer to Reviewer 1}

\begin{enumerate}

\item \emph{The utility of this tool beyond the experiments presented here is not apparent because the flexibility of the system was not demonstrated, for example:
- SimScene itself was only used in the first experiment, and other applications of it were not considered. Design choices vary widely between researchers and domains, meaning that the specific instantiations here may not be generally useful.}

@@

$\rightarrow$

\item \emph{It is not clear how this tool would be expanded to consider other acoustic parameters of interest, beyond level. It might be useful to consider potential relationships to other soundscape softwares such as TAPESTREA, and how the exploration of other acoustic parameters could be made intuitive for experiment participants.}

$\rightarrow$ The work of Misra \& al is indeed very relevant. A new Section (number 6) is now dedicated to this comparison with state-of-the-art approaches.

@@

\item \emph{In the last sentence of the abstract, the distinction of 'physical descriptors' vs. 'global descriptors'  does not have enough context here to be informative.}

$\rightarrow$ This sentence have be rewritten to be more explicit: "acoustic pressure levels computed for specific sound sources better characterize the appraisal than the acoustic pressure level computed over the overall soundscape."

### 2018-06-26 lafaySimulatedScenePerception.tex
adressing editor comments

  \begin{abstract}
    This paper introduces a new experimental protocol to study mental representations of urban soundscapes through a simulation process. Subjects are asked to create a full soundscape by means of a dedicated software tool, coupled with a structured sound data set. This paradigm is used to characterize urban sound environment representations by analyzing the sound classes that were used to simulate the auditory scenes. A rating experiment of the soundscape pleasantness using a 7-point bipolar semantic scale is conducted to further refine the analysis of the simulated urban acoustic scenes. Results show that 1) a semantic characterization in terms of presence~/ absence of sound sources is an effective way to characterize urban soundscapes pleasantness, and 2) physical descriptors computed for specific sound sources better characterize the appraisal than global descriptors.
  \end{abstract}

@@

@@

>>>>

  \begin{abstract}
    This paper introduces a new experimental protocol to study mental representations of urban soundscapes through a simulation process. Subjects are asked to create a full soundscape by means of a dedicated software tool, coupled with a structured sound data set. This paradigm is used to characterize urban sound environment representations by analyzing the sound classes that were used to simulate the auditory scenes. A rating experiment of the soundscape pleasantness using a 7-point bipolar semantic scale is conducted to further refine the analysis of the simulated urban acoustic scenes. Results show that 1) a semantic characterization in terms of presence~/ absence of sound sources is an effective way to characterize urban soundscapes pleasantness, and 2) acoustic pressure levels computed for specific sound sources better characterize the appraisal than the acoustic pressure level computed over the overall soundscape.
  \end{abstract}

@@

%\subsection{Discussion}

@@

\section{Related computational approaches}

Considering sound scene synthesis or composition as part of an experimental protocol requires the availability of software resources that are easier and easier to master. While most processing framework that have been considered are developed in native language for efficiency purposes like Marsyas \cite{tzanetakis2000marsyas} or Clam \cite{amatriain2006clam}, many advanced sound manipulation.

Closer to our sound model is the Tapestrea framework \cite{misra2007musical} that allows the manipulation sounds trough wavelet and sinusoidal modeling to allow sound manipulations for doing acousmatic composition or sound
design. The main issue with considering this framework for soundscape perception studies is that the sounds are processed using sound models that would strongly decrease the ecological validity of the study. That being said, the sequencing model is quite close to the one considered in this study.

The experiments described here does not introduce yet another sound manipulation framework and is thus not designed to be extensible. Rather it is considered here to demonstrate the following:
\begin{itemize}
  \item the use of Webaudio javascript library is useful to design advanced experimental protocols that consider sound manipulation over the web
  \item the soundscape model considered is useful to question important research questions within the soundscape community  but simple enough to be grasped by novice participants.
\end{itemize}

Extensions to other sound parameters beyond acoustic levels and . However, the control of those new parameters would need a specific user experience study to maintain a high degree of usability of the controlling interface.
